\textbf{EECS 340: Assignment 6}

### 2020-04-21 assignment_6/article.tex
✨ Add Problem 2 response.

>>>>

\textbf{Greedy choice property}: In some optimal solutions, the activity with the earliest deadline is scheduled first.

Let $S$ be an arbitrarily picked optimal solution, let event $E$ being the activity with the earlist deadline, let event $F$ being the firstly scheduled activity in $S$. We may have two cases:
\begin{itemize}
    \item $E$ is the same activity as $F$, then the property is proven.
    \item $E$ is not the same activity as $F$, which means $F$ is scheduled ealier than $E$. Now we may form a solution $S'$ by swapping the order of $E$ with any activities scheduled before $E$, until $E$ swaps with $F$ (after such swap $E$ should be the firstly scheduled activity in $S$).
\end{itemize}

We may safely perform such swap(s) in the latter case due to the fact that such swap will have no effect on the \textit{maximum delay} time. For any activity $i$ to be scheduled, let $\Delta_i$ and $\Delta'_i$ represent its delay in solution $S$ and $S'$ respectively. The only case that we will have $\Delta'_i > \Delta_i$ is if activity $i$ is scheduled before $E$ in $S$ (thus after swaps, scheduled after $E$ in $S'$, and caused even more delay). In such scenario we may have:

\begin{align*}
    \Delta'_i &= \Delta_i + t_E = f_i - d_i + t_E \\
    &\leq s_E + t_E - d_i \\
    &= f_E - d_i \\
    &\leq f_E - d_e = \Delta_E \\
    &\Longrightarrow \ \Delta'_i \leq \Delta_E
\end{align*}

Since we know that the maximum delay in $S$ must be $\geq \Delta_E$ (for either $E$ causing the maximum delay or some other activity), and also since $\Delta'_i$ is calculated from arbitrarily picked $i$ in $S'$, we may conclude that the maximum delay in $S'$ will not be larger than the maximum delay in $S$. Consider $S$ is set to be optimal -- meaning its maximum maximum delay cannot get any shorter -- we must be $\Delta S'_{\text{max}} = \Delta S_{\text{max}}$; which means $S'$ is also optimal. And since $E$ is the firstly scheduled activity in $S'$, we have proven the greedy choice property to be valid.
